\chapter{Referências Bibliográficas}
\label{ch:referencias}

\begin{thebibliography}{99}

\bibitem{beck1979} Beck, A. T. (1979). \textit{Cognitive Therapy and the Emotional Disorders}. Penguin Books.

\bibitem{brecht1964} Brecht, B. (1964). \textit{Brecht on Theatre: The Development of an Aesthetic} (J. Willett, Ed. \& Trans.). Hill and Wang.

\bibitem{chomsky1965} Chomsky, N. (1965). \textit{Aspects of the Theory of Syntax}. MIT Press.

\bibitem{dennett1991} Dennett, D. C. (1991). \textit{Consciousness Explained}. Little, Brown and Company.

\bibitem{dostoievski1866} Dostoiévski, F. (1866). \textit{Crime e Castigo} (C. E. Pereira, Trans.). Editora 34.

\bibitem{dreyfus1972} Dreyfus, H. L. (1972). \textit{What Computers Can't Do: A Critique of Artificial Reason}. Harper \& Row.

\bibitem{erickson1979} Erickson, M. H., \& Rossi, E. L. (1979). \textit{Hypnotherapy: An Exploratory Casebook}. Irvington Publishers.

\bibitem{foucault1969} Foucault, M. (1969). \textit{The Archaeology of Knowledge} (A. M. Sheridan Smith, Trans.). Pantheon Books.

\bibitem{frankl1959} Frankl, V. E. (1959). \textit{Man's Search for Meaning}. Beacon Press.

\bibitem{freire1970} Freire, P. (1970). \textit{Pedagogy of the Oppressed} (M. B. Ramos, Trans.). Continuum.

\bibitem{freud1900} Freud, S. (1900). \textit{The Interpretation of Dreams} (J. Strachey, Trans.). Basic Books.

\bibitem{guimaraes1956} Guimarães Rosa, J. (1956). \textit{Grande Sertão: Veredas}. José Olympio.

\bibitem{habermas1984} Habermas, J. (1984). \textit{The Theory of Communicative Action, Vol. 1: Reason and the Rationalization of Society} (T. McCarthy, Trans.). Beacon Press.

\bibitem{hayes1999} Hayes, S. C., Strosahl, K. D., \& Wilson, K. G. (1999). \textit{Acceptance and Commitment Therapy: An Experiential Approach to Behavior Change}. Guilford Press.

\bibitem{hegel1807} Hegel, G. W. F. (1807). \textit{Phenomenology of Spirit} (A. V. Miller, Trans.). Oxford University Press.

\bibitem{kafka1915} Kafka, F. (1915). \textit{A Metamorfose} (M. Carone, Trans.). Companhia das Letras.

\bibitem{klein1975} Klein, M. (1975). \textit{Envy and Gratitude and Other Works 1946-1963}. The Hogarth Press.

\bibitem{lacan1966} Lacan, J. (1966). \textit{Écrits} (B. Fink, Trans.). W. W. Norton \& Company.

\bibitem{linehan1993} Linehan, M. M. (1993). \textit{Cognitive-Behavioral Treatment of Borderline Personality Disorder}. Guilford Press.

\bibitem{lispector1964} Lispector, C. (1964). \textit{A Paixão Segundo G.H}. Editora do Autor.

\bibitem{marx1932} Marx, K., \& Engels, F. (1932). \textit{The German Ideology} (C. J. Arthur, Ed.). International Publishers.

\bibitem{nicolelis2011} Nicolelis, M. (2011). \textit{Beyond Boundaries: The New Neuroscience of Connecting Brains with Machines---and How It Will Change Our Lives}. Times Books.

\bibitem{nietzsche1883} Nietzsche, F. (1883). \textit{Thus Spoke Zarathustra} (W. Kaufmann, Trans.). Penguin Books.

\bibitem{rogers1951} Rogers, C. R. (1951). \textit{Client-Centered Therapy: Its Current Practice, Implications, and Theory}. Houghton Mifflin.

\bibitem{saramago1995} Saramago, J. (1995). \textit{Ensaio sobre a Cegueira}. Editorial Caminho.

\bibitem{saussure1916} Saussure, F. (1916). \textit{Course in General Linguistics} (C. Bally \& A. Sechehaye, Eds.; W. Baskin, Trans.). McGraw-Hill.

\bibitem{searle1983} Searle, J. R. (1983). \textit{Intentionality: An Essay in the Philosophy of Mind}. Cambridge University Press.

\bibitem{spinoza1677} Spinoza, B. (1677). \textit{Ethics} (E. Curley, Trans.). Penguin Classics.

\bibitem{vygotsky1934} Vygotsky, L. S. (1934). \textit{Thought and Language} (E. Hanfmann \& G. Vakar, Trans.). MIT Press.

\bibitem{wiener1948} Wiener, N. (1948). \textit{Cybernetics: Or Control and Communication in the Animal and the Machine}. MIT Press.

\bibitem{wittgenstein1922} Wittgenstein, L. (1922). \textit{Tractatus Logico-Philosophicus} (C. K. Ogden, Trans.). Kegan Paul.

\bibitem{wittgenstein1953} Wittgenstein, L. (1953). \textit{Philosophical Investigations} (G. E. M. Anscombe, Trans.). Basil Blackwell.

\end{thebibliography}
